An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-03-04 Article/EconGrowth2.Rnw
moving constants from pacakge to Rnw file

>>>>

<<constants, include=FALSE>>=
# Graph Heights
#' @export
maxHeight <- 8.5 # Inches
#' @export
ninePanelScatterGraphHeight <- maxHeight # Inches
#' @export
ninePanelTernaryGraphHeight <- 7 # Inches
#' @export
ninePanelSpaghettiGraphHeight <- 7 # Inches

# Graph Widths
#' @export
maxWidth <- 6.5 # Inches
#' @export
fourPanelScatterGraphWidth <- maxWidth # Inches
#' @export
threePanelScatterGraphWidth <- maxWidth*0.75 # Inches
#' @export
onePanelScatterGraphWidth <- maxWidth*0.25
#' @export
fourPanelTernaryGraphWidth <- maxWidth
#' @export
twoPanelTernaryGraphWidth <- maxWidth*0.45
#' @export
fourPanelSpaghettiGraphWidth <- maxWidth
#' @export
twoPanelSpaghettiGraphWidth <- maxWidth*0.55
#' @export
onePanelSpaghettiGraphWidth <- maxWidth*0.4

#' @export
presentationGraph1RowHeight <- 2.8 # Inches
#' @export
presentationGraph2ColWidth <- 2 # Inches
#' @export
presentationGraph1ColWidth <- 2*presentationGraph2ColWidth
#' @export
keyTextSize <- 0.85 # 85% of normal size
#' @export
keyColumns <- 1 # Want only 1 column in the key for lattice graphs
#' @export
defaultKeyXLoc <- 0.01 # x position of the key. This default is good for 9-panel graphs.
#' @export
defaultKeyYLoc <- 0.95 # y position of the key. This default is good for 9-panel graphs.
# Parameter graphs are tricky to ensure same size. I've found that with height set to 5 in for the 
# cd graphs and 2.93 in for the sf graphs, I get a nearly-exact match with graph size. From these settings I 
# can set up 2 equations:
#    5 in = 2*hgraph + haxis
#    2.93 in = hgraph + haxis
# to estimate that h_axis = 0.86 in and hgraph = 2.05 in.
#' @export
h_param_graph <- 2.07 # Inches for a single panel
#' @export
h_param_axis <- 0.86 # Inches (also includes whatever margin is applied)
#' @export
sfParameterGraphHeight <- h_param_graph + h_param_axis
#' @export
cdParameterGraphHeight <- 2*h_param_graph + h_param_axis
#' @export
cesParameterGraphHeight <- 3*h_param_graph + h_param_axis
#' @export
linexParameterGraphHeight <- h_param_graph + h_param_axis
#' @export
sfParameterGraphWidth <- maxWidth
#' @export
cdParameterGraphWidth <- maxWidth
#' @export
cdTernaryGraphWidth <- maxWidth/2.2
#' @export
cdSpaghettiGraphWidth <- maxWidth/2.2
#' @export
cesParameterGraphWidth <- maxWidth
#' @export
linexParameterGraphWidth <- maxWidth
# Other graph parameters that apply to all graphs
#' @export
scaleTextSize <- 0.8  # Multiple of normal size
#' @export
scaleTickSize <- -0.5 # 50% of normal size and pointing INWARD!

@
